simulation_study_spline

### 2025-01-08 R/simulation_study_CRCVM/CRCVM_examples/illustrative_trajectories.Rmd
new set up for simulation study on clusters

  res=sim_CRCVM(ftau=ftau_constant,fomega=fomega_minimal,fnu=fnu_constant,v0=v0,x0=x0[i,],
                    times=times,land=rect_border,verbose=FALSE)

@@

```{r simulate with omega cubic in rectangle,cache=TRUE}

@@

```{r simulate with omega cubic in rectangle,cache=TRUE}

>>>>

  res=sim_CRCVM(ftau=ftau_constant,fomega=fomega_tanh,fnu=fnu_constant,v0=v0,x0=x0[i,],
                    times=times,land=rect_border,verbose=FALSE)

@@

```{r simulate with omega cubic attractive in rectangle,cache=TRUE}

@@

```{r simulate with omega cubic repulsive in rectangle,cache=TRUE}

### 2025-01-08 R/simulation_study_CRCVM/spline_estimation_local/simulation_study_spline.Rmd
new set up for simulation study on clusters

ggplot(data_lf_he)+geom_histogram(aes(x=speed),bins=30)+facet_wrap(~ID)+theme_minimal()
quantile(data_lf_he$speed,na.rm=TRUE)
```

@@

cropped_data=data_lf_he[data_lf_he$ID %in% 1:3,]

H=array(rep(SIGMA_OBS_high^2*diag(2),length(cropped_data$time)),dim=c(2,2,length(cropped_data$time)))

@@

crcvm_splines_lf_he$update_map(list("log_lambda"=factor(rep(NA,2))))
crcvm_splines_lf_he$update_lambda(c(10^-7,10^-13))
#fit
crcvm_splines_lf_he$fit(method="BFGS")
```

>>>>

ggplot(data_lf_he)+geom_histogram(aes(x=speed),bins=30)+facet_wrap(~ID)+theme_minimal()
quantile(data_lf_he$speed,na.rm=TRUE)
```
```{r}
ggplot(data_lf_he)+geom_histogram(aes(x=theta),bins=30)+facet_wrap(~ID)+theme_minimal()
```

@@

H=array(rep(SIGMA_OBS_high^2*diag(2),length(data_lf_he$time)),dim=c(2,2,length(data_lf_he$time)))

formulas <- list(mu1=~1,mu2=~1,tau=~s(theta,k=8,bs="cc"),
                 nu=~1,omega=~te(theta,DistanceShore,k=SP_DF,bs="cs"))

@@

crcvm_splines_lf_he$update_map(list("log_lambda"=factor(c(1,rep(NA,2)))))
crcvm_splines_lf_he$update_lambda(c(1,10^-7,10^-13))
#fit
crcvm_splines_lf_he$fit(method="BFGS")
```
